Supplementary Appendix

### 2023-07-12 manuscript/supplement.qmd
added one more amazing Git resource
corrected link

## Example for an end-to-end workflow using Git

@@

@@

    -   Division of Pharmacoepidemiology and Pharmacoeconomics: [https://gitlab-scm.partners.org/drugepi](https://gitlab-scm.partners.org/drugepi/harper){.uri}

>>>>

## Example for an end-to-end workflow cycle using Git

@@

-   Comprehensive guide on the use of Git in combination with R: <https://happygitwithr.com/>

@@

    -   Division of Pharmacoepidemiology and Pharmacoeconomics: <https://gitlab-scm.partners.org/drugepi>
